\vspace{-1in} Demystifying the Computer Science \\PhD Admission in US Universities\\{\large A guide for Vietnamese and International Students

### 2023-06-17 phd-cs-us.tex
Updates from Overleaf

The primary focus of the admissions committee is to \textbf{evaluate your background and interest in research} since a PhD in Computer Science
is a research degree and determine if you would \textbf{fit} the program. To evaluate your profile, we consider
the following key indicators, listed in order of importance.

@@

>>>>

The primary focus of the admissions committee is to \textbf{evaluate your background and interest in research} since a PhD in Computer Science and determine if you would \textbf{fit into} the program. To evaluate your profile, we consider
the following key indicators, listed in order of importance.

@@

\subsection{Should you contact a US professor? How to do so "correctly"?}

\tvn{TODO: How to write an email that will get a reply?}
